The Tor Network - Strengths and Weaknesses \\ \Large Computer Security 1 - CS5460 \\ \LaTeX{}

### 2013-11-11 paper.tex
fixed syntax errors

Within the network, nodes talk to each other via the Transport Security Layer (TLS) protocol. When a circuit is built, each pair of nodes within it must first come to an agreement over an encryption key and the specific cipher to use for encryption. There are several mechanisms by which this can be done, all of which use Diffie-Hellman (DH) for key exchange. The most common methods include: TLS_RSA, which rely upon public and private keys generated with RSA; TLS_DHE, ephemeral DH; TLS_ECDH, DH based on elliptic curves, and TLS_ECDHE, ephemeral elliptic curve DH. It should be noted that only TLS_DHE and TLS_ECDHE provide perfect forward secrecy, so it is no surprise that Tor exclusively prefers them. Once encryption keys and the specific cipher (as well as its mode) have been agreed upon, communication of traffic between two nodes can be encrypted and exchanged.

@@

To generate the RSA keys, two distinct prime numbers of similar bit-length are chosen at random, \textit{p} and \textit{q}. \textit{n} is computed as the product of \textit{p} and \textit{q}, and it is used as the modulus for both the public and private keys. The bit-length of \textit{n} is the RSA key length. Then let φ(n)\; =\; φ(p) φ(q)\; =\; (p − 1) (q − 1)\; where φ is Euler's totient function, whcih counts the number of positive integers less than or equal to \textit{n} that are relatively prime to \textit{n}. Then \textit{e} is chosen such that \textit{e} and φ(n) are coprime. \textit{d} is also chosen such that it is the multiplicative inverse of e modulo φ(n). The RSA public key then consists of the modulus \textit{n} and the exponent \textit{e}. The private key likewise consists of \textit{n} and the exponent \textit{d}.

A message \textit{M} is encrypted by first blocks of length less than \textit{n} using an agreed-upon padding scheme. The ciphertext \textit{c} is then computed as m^e mod n, which can be calculated quickly using the method of exponentiation by squaring. The recipient (the owner of the private key) can then recover the plaintext \textit{M} by computing c^d mod n, and then reversing the padding scheme. The decryption process is often accelerated by optimizations such as the Chinese Remainder Theorem. Furthermore, to sign a message, the owner of the private key first uses an agreed-upon hash function to compute a hash value of the message, raises it to the power of \textit{d} modulo \textit{n} and then sends that in conjuction with \textit{M}. The recipient, who only has access to the public keys, then raises the signature to the power of \textit{e} modulo \textit{n} and compares the result with his hash of the message using the same hash algorithm. If the two match, then he can prove the authenticity and integrity of the message. These two capabilities make RSA an extremely powerful tool for securing authenticity, integrity, and privacy of communication between two parties.

@@

Elliptic curves over the real number system can be defined through the equation,
y^2\; =\; x^3\; +\; a x\; +\; b\;
Where \textit{a} and \textit{b} are real numbers. This formula describes a plane curve through the Euclidean plane, although elliptic curves do exists in other spaces. However, current cryptographic purposes only work with elliptic curves within the context of the real number systems.

@@

@@

% http://homes.cs.washington.edu/~yoshi/papers/Tor/PETS2008_37.pdf
\bibitem{McCoy2008}
  Damon McCoy, Kevin Bauer, Dirk Grunwald, Tadayoshi Kohno, Douglas Sicker,
  \emph{\LaTeX: Shining Light in Dark Places: Understanding the Tor Network}.
  Department of Computer Science and Engineering,
  University of Washington, Seattle, WA 98195-2969,
  2008.

% http://delivery.acm.org/10.1145/1320000/1314336/p11-bauer.pdf?ip=129.123.212.2&id=1314336&acc=ACTIVE%20SERVICE&key=C2716FEBFA981EF14CED21A2601DAAECFD63F9AFA4F38248&CFID=375634674&CFTOKEN=21383502&__acm__=1383519744_1cd525050cafbe9ffe083b269ff783d9
\bibitem{Bauer2007}
  Kevin Bauer, Damon McCoy, Dirk Grunwald, Tadayoshi Kohno, Douglas Sicker
  \emph{\LaTeX: Low-resource routing attacks against tor}.
  ACM, 2007

% http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5636000&tag=1
\bibitem{Chaabane2007}
  Abdelberi Chaabane, Pere Manils, Mohamed Ali Kaafar
  \emph{\LaTeX: Digging into Anonymous Trafﬁc: a deep analysis of the Tor anonymizing network}.
  IEEE, 2010

@@

% http://www.nsa.gov/business/programs/elliptic_curve.shtml
\bibitem{CaseForECC}
  National Security Agency
  \emph{\LaTeX: The Case for Elliptic Curve Cryptography}.
  NSA, 2009

% http://blog.erratasec.com/2013/09/tor-is-still-dhe-1024-nsa-crackable.html
% http://thehackernews.com/2013/09/NSA-can-crack-TOR-Encryptio-Snowden-files-.html
\bibitem{Graham2013}
  Robert Graham
  \emph{\LaTeX: Tor is still DHE 1024 (NSA crackable)}.
  Errata Security, 2013

>>>>

Within the network, nodes talk to each other via the Transport Security Layer (TLS) protocol. When a circuit is built, each pair of nodes within it must first come to an agreement over an encryption key and the specific cipher to use for encryption. There are several mechanisms by which this can be done, all of which use Diffie-Hellman (DH) for key exchange. The most common methods include: TLS\_RSA, which rely upon public and private keys generated with RSA; TLS\_DHE, ephemeral DH; TLS\_ECDH, DH based on elliptic curves, and TLS\_ECDHE, ephemeral elliptic curve DH. It should be noted that only TLS\_DHE and TLS\_ECDHE provide perfect forward secrecy, so it is no surprise that Tor exclusively prefers them. Once encryption keys and the specific cipher (as well as its mode) have been agreed upon, communication of traffic between two nodes can be encrypted and exchanged.

@@

To generate the RSA keys, two distinct prime numbers of similar bit-length are chosen at random, \textit{p} and \textit{q}. \textit{n} is computed as the product of \textit{p} and \textit{q}, and it is used as the modulus for both the public and private keys. The bit-length of \textit{n} is the RSA key length. Then let φ(n)\; =\; φ(p) φ(q)\; =\; (p − 1) (q − 1)\; where φ is Euler's totient function, which counts the number of positive integers less than or equal to \textit{n} that are relatively prime to \textit{n}. Then \textit{e} is chosen such that \textit{e} and φ(n) are coprime. \textit{d} is also chosen such that it is the multiplicative inverse of e modulo φ(n). The RSA public key then consists of the modulus \textit{n} and the exponent \textit{e}. The private key likewise consists of \textit{n} and the exponent \textit{d}.

A message \textit{M} is encrypted by first blocks of length less than \textit{n} using an agreed-upon padding scheme. The ciphertext \textit{c} is then computed as m\^e mod n, which can be calculated quickly using the method of exponentiation by squaring. The recipient (the owner of the private key) can then recover the plaintext \textit{M} by computing c\^d mod n, and then reversing the padding scheme. The decryption process is often accelerated by optimizations such as the Chinese Remainder Theorem. Furthermore, to sign a message, the owner of the private key first uses an agreed-upon hash function to compute a hash value of the message, raises it to the power of \textit{d} modulo \textit{n} and then sends that in conjuction with \textit{M}. The recipient, who only has access to the public keys, then raises the signature to the power of \textit{e} modulo \textit{n} and compares the result with his hash of the message using the same hash algorithm. If the two match, then he can prove the authenticity and integrity of the message. These two capabilities make RSA an extremely powerful tool for securing authenticity, integrity, and privacy of communication between two parties.

@@

Elliptic curves over the real number system can be defined through the equation,
y\^2\; =\; x\^3\; +\; a x\; +\; b\;
Where \textit{a} and \textit{b} are real numbers. This formula describes a plane curve through the Euclidean plane, although elliptic curves do exists in other spaces. However, current cryptographic purposes only work with elliptic curves within the context of the real number systems.

@@

\section{Features}

\subsection{SOCKS}

The Tor client software offers a Secure Sockets (SOCKS) interface on the system's localhost. SOCKS is different than HTTP proxying, although it uses handshake protocols for authorization purposes, it does not interpret or rewrite any of the subsequent traffic. The Tor Browser Bundle uses this interface as an input to the Tor network, although other applications may also utilize it. SOCKS then multiplexes traffic through the Tor circuit.

\subsection{Hidden services}

%https://en.wikipedia.org/wiki/Core.onion
%https://en.wikipedia.org/wiki/DuckDuckGo
%https://en.wikipedia.org/wiki/The_Hidden_Wiki

@@

% http://homes.cs.washington.edu/~yoshi/papers/Tor/PETS2008_37.pdf
\bibitem{McCoy2008}
  Damon McCoy, Kevin Bauer, Dirk Grunwald, Tadayoshi Kohno, Douglas Sicker,
  \emph{Shining Light in Dark Places: Understanding the Tor Network}.
  Department of Computer Science and Engineering,
  University of Washington, Seattle, WA 98195-2969,
  2008.

% http://delivery.acm.org/10.1145/1320000/1314336/p11-bauer.pdf?ip=129.123.212.2&id=1314336&acc=ACTIVE%20SERVICE&key=C2716FEBFA981EF14CED21A2601DAAECFD63F9AFA4F38248&CFID=375634674&CFTOKEN=21383502&__acm__=1383519744_1cd525050cafbe9ffe083b269ff783d9
\bibitem{Bauer2007}
  Kevin Bauer, Damon McCoy, Dirk Grunwald, Tadayoshi Kohno, Douglas Sicker
  \emph{Low-resource routing attacks against tor}.
  ACM, 2007

% http://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=5636000&tag=1
\bibitem{Chaabane2007}
  Abdelberi Chaabane, Pere Manils, Mohamed Ali Kaafar
  \emph{Digging into Anonymous Trafﬁc: a deep analysis of the Tor anonymizing network}.
  IEEE, 2010

@@

% http://www.nsa.gov/business/programs/elliptic_curve.shtml
\bibitem{CaseForECC}
  National Security Agency
  \emph{The Case for Elliptic Curve Cryptography}.
  NSA, 2009

% http://blog.erratasec.com/2013/09/tor-is-still-dhe-1024-nsa-crackable.html
% http://thehackernews.com/2013/09/NSA-can-crack-TOR-Encryptio-Snowden-files-.html
\bibitem{Graham2013}
  Robert Graham
  \emph{Tor is still DHE 1024 (NSA crackable)}.
  Errata Security, 2013
